---
title: "Gating strategy"
author: "mwitmond"
date: "2023-03-08"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 3
    code_folding: hide
editor_options:
  chunk_output_type: console
---


## Set-up

```{r setup, message=F, warning=F}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_FACS.R", local = knitr::knit_global())
```

```{r fig_settings}
row_order = c("A", "B", "C", "D", "E", "F", "G", "H")
col_order = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
panel_labels <- c("a", "b", "c","d", "e", "f", "g", "h", "i", "j", "k", "l", "m")

textsize <- theme(axis.text = element_text(colour = "black", size = 11), #, face = "bold"
                  axis.title = element_text(colour = "black", size = 12), 
                  legend.title = element_text(colour = "black", size = 12),
                  # legend.title = element_blank(), 
                  legend.text = element_text(colour = "black", size = 11), 
                  strip.text.x = element_text(colour = "black", size = 12)
)

textsize_small <- theme(text = element_text(size = 9, family = "sans", colour = "black"),
                        plot.title = element_text(size = 10)
)

colors_dark9 <- c("#4daf4a", "#984ea3", "#ffff33", "#ff7f00", "#e41a1c", "#f781bf", "#a65628", "#999999", "#377eb8")
colors_light12 <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5","#d9d9d9","#bc80bd","#ccebc5","#ffed6f")
```



## DS085: LinGradient_Conc

### Data

Read the .fcs files and create a FlowSet object with metadata
```{r data_DS085}
# Read files with the FlowSet function
fs_A_DS085 <- read.flowSet(path = "data/DS085_LinGradient_Conc/fcs_plateA", pattern = ".fcs", alter.names = T)
fs_B_DS085 <- read.flowSet(path = "data/DS085_LinGradient_Conc/fcs_plateB", pattern = ".fcs", alter.names = T)
```

```{r metadata_DS085}
# Extract information on wellID, row and column from the file name
# Format of file name: wellID_number_date_time.fcs
# Plate A
pData(fs_A_DS085)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_A_DS085))
pData(fs_A_DS085)$rowID <- gsub("(.).*", "\\1", pData(fs_A_DS085)$wellID)
pData(fs_A_DS085)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_A_DS085)$wellID))
pData(fs_A_DS085)$expID <- "DS085"
pData(fs_A_DS085)$plateID <- "A"

kable(pData(fs_A_DS085) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))

# Plate B
pData(fs_B_DS085)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_B_DS085))
pData(fs_B_DS085)$rowID <- gsub("(.).*", "\\1", pData(fs_B_DS085)$wellID)
pData(fs_B_DS085)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_B_DS085)$wellID))
pData(fs_B_DS085)$expID <- "DS085"
pData(fs_B_DS085)$plateID <- "B"

kable(pData(fs_B_DS085) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))

fs_DS085 <- rbind2(fs_A_DS085, fs_B_DS085)
```


### Debris

Define the gate on debris (SSC-A vs FSC-A): Exclude the lower left data points and those data point that fall at/off the upper and right edges of the plot
```{r debris_DS085, fig.width=5, fig.height=4}
# Create a GatingSet object from the FlowSet object
gs_DS085 <- GatingSet(fs_DS085)

# Manually adjust the numbers and check in the graph to set the right gate
g_debris_DS085 <- polygonGate(filterId = "Debris", "FSC.A" = c(4e4, 26e4, 26e4, 1e5), "SSC.A" = c(1e4, 1e4, 26e4, 26e4)) # define gate

ggcyto(gs_DS085[[1]], aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 200) +
  geom_gate(g_debris_DS085) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs cell complexity and debris gate. One exemplary sample.*  

```{r fig_debris_DS085, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS085, g_debris_DS085)
recompute(gs_DS085)

# Plate A
ggcyto(subset(gs_DS085, plateID == "A"), aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS085, plateID == "B"), aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Singlets

Define the gate on singlets (FSC-W vs FSC-H): Exclude all data points that do not fall in the mass of data points
```{r singlets_DS085, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_singlets_DS085 <- polygonGate(filterId = "Singlets", "FSC.H" = c(3e4, 6.5e4, 7.5e4, 2.5e4), "FSC.W" = c(8e4, 9e4, 1.4e5, 1.4e5)) # define gate

ggcyto(gs_DS085[[1]], aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 200) +
  geom_gate(g_singlets_DS085) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size height vs cell size width and singlet cell gate. One exemplary sample.* 

```{r fig_singlets_DS085, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS085, g_singlets_DS085, parent = "Debris")
recompute(gs_DS085) 

# Plate A
ggcyto(subset(gs_DS085, plateID == "A"), aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS085, plateID == "B"), aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Live cells (fixed)

Define the gate on live/dead (fixed) cells (BV421 vs FSC-A): Exclude the upper data points and those data point that fall at/off the right edges of the plot
```{r live_DS085, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_live_DS085 <- polygonGate(filterId = "Live", "FSC.A" = c(4.4e4, 1.6e5, 1.6e5, 4.4e4), "BV421.A" = c(1e2, 1e2, 5e3, 2e3)) # define gate

ggcyto(gs_DS085[[1]], aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 200) +
  geom_gate(g_live_DS085) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e0, 5e4)) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs live/death stain and live cell gate. One exemplary sample.* 

```{r fig_live_DS085, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS085, g_live_DS085, parent = "Singlets")
recompute(gs_DS085) 

# Plate A
ggcyto(subset(gs_DS085, plateID == "A"), aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e1, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS085, plateID == "B"), aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e1, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Summary

```{r gating_DS085}
# Remove previous file if it exist
if(file.exists(paste0("output/", "gated_data_DS085"))) {
  unlink(paste0("output/", "gated_data_DS085"), recursive = TRUE)
}

# Save dataset
save_gs(gs_DS085, path = paste0("output/", "gated_data_DS085"))

gc()

# Gating strategy
plot(gs_DS085, bool = TRUE)
```
***Figure:** Gating strategy.* 


### Population statistics

```{r cell_counts_DS085}
# Get cell counts
counts_DS085 <- gs_pop_get_count_fast(gs_DS085)
counts_DS085 <- merge(counts_DS085, pData(fs_DS085), by = "name")
counts_DS085$PercentParent <- (counts_DS085$Count / counts_DS085$ParentCount) * 100

# Calculate percentage from root
counts_root_DS085 <- counts_DS085 %>% filter(Parent == "root") %>% select(name, RootCount = ParentCount)
counts_DS085 <- left_join(counts_DS085, counts_root_DS085)
counts_DS085$PercentRoot <- (counts_DS085$Count / counts_DS085$RootCount) * 100

# Save the number of cells per well per gate as .csv file
counts_save_DS085 <- counts_DS085[ , c("plateID", "wellID", "name", "Population", "Count", "ParentCount", "PercentParent", "RootCount", "PercentRoot")]
write_csv(counts_save_DS085, file = "output/gated_counts_DS085.csv")
```

```{r fig_cells_DS085, fig.width=6, fig.height=4}
# Plate A
counts_final_A_DS085 <- subset(counts_DS085, Population == "/Debris/Singlets/Live" & plateID == "A")
raw_map(data = counts_final_A_DS085$Count, well = counts_final_A_DS085$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts (plate A)") +
  theme_bw() +
  textsize

# Plate B
counts_final_B_DS085 <- subset(counts_DS085, Population == "/Debris/Singlets/Live" & plateID == "B")
raw_map(data = counts_final_B_DS085$Count, well = counts_final_B_DS085$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts (plate B)") +
  theme_bw() +
  textsize
```
***Figure:** Number of live single cells after gating (counts per sample/well).* 

```{r live_cells_DS085}
percent_live_DS085 <- subset(counts_DS085, Population == "/Debris/Singlets/Live")[, c("name", "plateID", "wellID", "PercentRoot")]

# Add metadata per well from custom .csv file
metadata_DS085 <- read_csv("data/DS085_LinGradient_Conc/metadata_plate_DS085.csv")
percent_live_DS085 <- left_join(percent_live_DS085, metadata_DS085)
```

```{r fig_live_percent_DS085, fig.width=6, fig.height=4}
ggplot(subset(percent_live_DS085, staining == "yes"), aes(x = time_min, y = PercentRoot)) +
  geom_point(aes(color = factor(stim_description)), size = 2) +
  facet_wrap(~plateID, ncol = 2) +
  ylim(0, 100) +
  scale_x_continuous() +
  scale_color_manual(
    values = colors_dark9[1:4],
    breaks = unique(percent_live_DS085$stim_description),
    name = "",
  ) +
  labs(y = "Percentage live single \ncells from root (%)", x = "Stimulation time (min)") +
  theme_bw() +
  theme(legend.position = "bottom", legend.justification = "right") +
  guides(color = guide_legend(nrow = 2, bycol = TRUE)) +
  textsize
```
***Figure:** Percentage of live single cells from root.*



## DS095: DetailedStep_Conc

### Data

Read the .fcs files and create a FlowSet object with metadata
```{r data_DS095}
# Read files with the FlowSet function
fs_A_DS095 <- read.flowSet(path = "data/DS095_DetailedStep_Conc/fcs_plateA", pattern = ".fcs", alter.names = T)
fs_B_DS095 <- read.flowSet(path = "data/DS095_DetailedStep_Conc/fcs_plateB", pattern = ".fcs", alter.names = T)
fs_C_DS095 <- read.flowSet(path = "data/DS095_DetailedStep_Conc/fcs_plateC", pattern = ".fcs", alter.names = T)
```

```{r metadata_DS095}
# Extract information on wellID, row and column from the file name
# Format of file name: wellID_number_date_time.fcs
# Plate A
pData(fs_A_DS095)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_A_DS095))
pData(fs_A_DS095)$rowID <- gsub("(.).*", "\\1", pData(fs_A_DS095)$wellID)
pData(fs_A_DS095)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_A_DS095)$wellID))
pData(fs_A_DS095)$expID <- "DS095"
pData(fs_A_DS095)$plateID <- "A"

kable(pData(fs_A_DS095) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))

# Plate B
pData(fs_B_DS095)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_B_DS095))
pData(fs_B_DS095)$rowID <- gsub("(.).*", "\\1", pData(fs_B_DS095)$wellID)
pData(fs_B_DS095)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_B_DS095)$wellID))
pData(fs_B_DS095)$expID <- "DS095"
pData(fs_B_DS095)$plateID <- "B"

kable(pData(fs_B_DS095) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))

# Plate C
pData(fs_C_DS095)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_C_DS095))
pData(fs_C_DS095)$rowID <- gsub("(.).*", "\\1", pData(fs_C_DS095)$wellID)
pData(fs_C_DS095)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_C_DS095)$wellID))
pData(fs_C_DS095)$expID <- "DS095"
pData(fs_C_DS095)$plateID <- "C"

kable(pData(fs_C_DS095) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))

fs_AB_DS095 <- rbind2(fs_A_DS095, fs_B_DS095)
fs_DS095 <- rbind2(fs_AB_DS095, fs_C_DS095)
```


### Debris

Define the gate on debris (SSC-A vs FSC-A): Exclude the lower left data points and those data point that fall at/off the upper and right edges of the plot
```{r debris_DS095, fig.width=3, fig.height=3}
# Create a GatingSet object from the FlowSet object
gs_DS095 <- GatingSet(fs_DS095)

# Manually adjust the numbers and check in the graph to set the right gate
g_debris_DS095 <- polygonGate(filterId = "Debris", "FSC.A" = c(4e4, 26e4, 26e4, 1e5), "SSC.A" = c(1e4, 1e4, 26e4, 26e4)) # define gate

fig_debris_DS095 <- ggcyto(gs_DS095[[1]], aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 200) +
  geom_gate(g_debris_DS095) +
  ggcyto_par_set(limits = "instrument") +
  facet_wrap(vars(factor(name, labels = "A01"))) + 
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris gate") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none")

# Save figure as png
ggsave(
  fig_debris_DS095,
  filename = "output/figures/gating_figs/fig_debris_DS095.png",
  width = 3,
  height = 3,
  units = "in",
  dpi = 300
  )
```
***Figure:** Cell size vs cell complexity and debris gate. One exemplary sample.*  

```{r fig_debris_DS095, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS095, g_debris_DS095)
recompute(gs_DS095)

# Plate A
ggcyto(subset(gs_DS095, plateID == "A"), aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS095, plateID == "B"), aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate C
ggcyto(subset(gs_DS095, plateID == "C"), aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root (plate C)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Singlets

Define the gate on singlets (FSC-W vs FSC-H): Exclude all data points that do not fall in the mass of data points
```{r singlets_DS095, fig.width=3, fig.height=3}
# Manually adjust the numbers and check in the graph to set right gate
g_singlets_DS095 <- polygonGate(filterId = "Singlets", "FSC.H" = c(3e4, 6.5e4, 7.5e4, 2.5e4), "FSC.W" = c(8e4, 9e4, 1.4e5, 1.4e5)) # define gate

fig_singlets_DS095 <- ggcyto(gs_DS095[[1]], aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 200) +
  geom_gate(g_singlets_DS095) +
  ggcyto_par_set(limits = "instrument") +
  facet_wrap(vars(factor(name, labels = "A01"))) + 
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets gate") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none")

# Save figure as png
ggsave(
  fig_singlets_DS095,
  filename = "output/figures/gating_figs/fig_singlets_DS095.png",
  width = 3,
  height = 3,
  units = "in",
  dpi = 300
  )
```
***Figure:** Cell size height vs cell size width and singlet cell gate. One exemplary sample.* 

```{r fig_singlets_DS095, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS095, g_singlets_DS095, parent = "Debris")
recompute(gs_DS095) 

# Plate A
ggcyto(subset(gs_DS095, plateID == "A"), aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS095, plateID == "B"), aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate C
ggcyto(subset(gs_DS095, plateID == "C"), aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris (plate C)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Live cells (fixed)

Define the gate on live/dead (fixed) cells (BV421 vs FSC-A): Exclude the upper data points and those data point that fall at/off the right edges of the plot
```{r live_DS095, fig.width=3, fig.height=3}
# Manually adjust the numbers and check in the graph to set right gate
g_live_DS095 <- polygonGate(filterId = "Live", "FSC.A" = c(4.4e4, 1.6e5, 1.6e5, 4.4e4), "BV421.A" = c(5e1, 5e1, 1e4, 3e3)) # define gate

fig_live_DS095 <- ggcyto(gs_DS095[[139]], aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 200) +
  geom_gate(g_live_DS095) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e0, 5e4)) +
  facet_wrap(vars(factor(name, labels = "A01"))) + 
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cell gate") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none")

# Save figure as png
ggsave(
  fig_live_DS095,
  filename = "output/figures/gating_figs/fig_live_DS095.png",
  width = 3,
  height = 3,
  units = "in",
  dpi = 300
  )
```
***Figure:** Cell size vs live/death stain and live cell gate. One exemplary sample.* 

```{r fig_live_DS095, fig.width=9, fig.height=7}
# Apply the gate to all data
gs_pop_add(gs_DS095, g_live_DS095, parent = "Singlets")
recompute(gs_DS095)

# Plate A
ggcyto(subset(gs_DS095, plateID == "A"), aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e1, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets (plate A)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate B
ggcyto(subset(gs_DS095, plateID == "B"), aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e1, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets (plate B)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize

# Plate C
ggcyto(subset(gs_DS095, plateID == "C"), aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e1, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets (plate C)") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Summary

```{r gating_DS095}
# Remove previous file if it exist
if(file.exists(paste0("output/", "gated_data_DS095"))) {
  unlink(paste0("output/", "gated_data_DS095"), recursive = TRUE)
}

# Save dataset
save_gs(gs_DS095, path = paste0("output/", "gated_data_DS095"))

gc()

# Gating strategy
plot(gs_DS095, bool = TRUE)
```
***Figure:** Gating strategy.* 


### Population statistics

```{r cell_counts_DS095}
# Get cell counts
counts_DS095 <- gs_pop_get_count_fast(gs_DS095)
counts_DS095 <- merge(counts_DS095, pData(fs_DS095), by = "name")
counts_DS095$PercentParent <- (counts_DS095$Count / counts_DS095$ParentCount) * 100

# Calculate percentage from root
counts_root_DS095 <- counts_DS095 %>% filter(Parent == "root") %>% select(name, RootCount = ParentCount)
counts_DS095 <- left_join(counts_DS095, counts_root_DS095)
counts_DS095$PercentRoot <- (counts_DS095$Count / counts_DS095$RootCount) * 100

# Save the number of cells per well per gate as .csv file
counts_save_DS095 <- counts_DS095[ , c("plateID", "wellID", "name", "Population", "Count", "ParentCount", "PercentParent", "RootCount", "PercentRoot")]
write_csv(counts_save_DS095, file = "output/gated_counts_DS095.csv")
```

```{r fig_cells_DS095, fig.width=6, fig.height=4}
# Plate A
counts_final_A_DS095 <- subset(counts_DS095, Population == "/Debris/Singlets/Live" & plateID == "A")
raw_map(data = counts_final_A_DS095$Count, well = counts_final_A_DS095$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts (plate A)") +
  theme_bw() +
  textsize

# Plate B
counts_final_B_DS095 <- subset(counts_DS095, Population == "/Debris/Singlets/Live" & plateID == "B")
raw_map(data = counts_final_B_DS095$Count, well = counts_final_B_DS095$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts (plate B)") +
  theme_bw() +
  textsize

# Plate C
counts_final_B_DS095 <- subset(counts_DS095, Population == "/Debris/Singlets/Live" & plateID == "C")
raw_map(data = counts_final_B_DS095$Count, well = counts_final_B_DS095$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts (plate C)") +
  theme_bw() +
  textsize
```
***Figure:** Number of live single cells after gating (counts per sample/well).* 

```{r live_cells_DS095}
percent_live_DS095 <- subset(counts_DS095, Population == "/Debris/Singlets/Live")[, c("name", "plateID", "wellID", "PercentRoot")]

# Add metadata per well from custom .csv file
metadata_DS095 <- read_csv("data/DS095_DetailedStep_Conc/metadata_plate_DS095.csv")
percent_live_DS095 <- left_join(percent_live_DS095, metadata_DS095)
```

```{r fig_live_percent_DS095, fig.width=6, fig.height=4}
ggplot(subset(percent_live_DS095, staining == "yes"), aes(x = time_min, y = PercentRoot)) +
  geom_point(aes(color = factor(H2O2_conc_mM)), size = 2) +
  facet_wrap(~plateID, ncol = 3) +
  ylim(0, 100) +
  scale_x_continuous() +
  scale_color_manual(
    values = colors_dark9,
    breaks = unique(percent_live_DS095$H2O2_conc_mM),
    name = "",
  ) +
  labs(y = "Percentage live single \ncells from root (%)", x = "Stimulation time (min)") +
  theme_bw() +
  theme(legend.position = "bottom", legend.justification = "right") +
  # guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
  textsize
```
***Figure:** Percentage of live single cells from root.*



## DS096: LinQuadGradient_HighConc

### Data

Read the .fcs files and create a FlowSet object with metadata
```{r data_DS096}
# Read files with the FlowSet function
fs_DS096 <- read.flowSet(path = "data/DS096_LinQuadGradient_HighConc/fcs", pattern = ".fcs", alter.names = T)
```

```{r metadata_DS096}
# Extract information on wellID, row and column from the file name
# Format of file name: wellID_number_date_time.fcs
pData(fs_DS096)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_DS096))
pData(fs_DS096)$rowID <- gsub("(.).*", "\\1", pData(fs_DS096)$wellID)
pData(fs_DS096)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_DS096)$wellID))
pData(fs_DS096)$expID <- "DS096"
pData(fs_DS096)$plateID <- "A"

kable(pData(fs_DS096) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Debris

Define the gate on debris (SSC-A vs FSC-A): Exclude the lower left data points and those data point that fall at/off the upper and right edges of the plot
```{r debris_DS096, fig.width=5, fig.height=4}
# Create a GatingSet object from the FlowSet object
gs_DS096 <- GatingSet(fs_DS096)

# Manually adjust the numbers and check in the graph to set the right gate
g_debris_DS096 <- polygonGate(filterId = "Debris", "FSC.A" = c(4e4, 26e4, 26e4, 1e5), "SSC.A" = c(1e4, 1e4, 26e4, 26e4)) # define gate

ggcyto(gs_DS096[[1]], aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 200) +
  geom_gate(g_debris_DS096) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs cell complexity and debris gate. One exemplary sample.*  

```{r fig_debris_DS096, fig.width=9, fig.height=6}
# Apply the gate to all data
gs_pop_add(gs_DS096, g_debris_DS096)
recompute(gs_DS096)

ggcyto(gs_DS096, aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Singlets

Define the gate on singlets (FSC-W vs FSC-H): Exclude all data points that do not fall in the mass of data points
```{r singlets_DS096, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_singlets_DS096 <- polygonGate(filterId = "Singlets", "FSC.H" = c(3e4, 6e4, 9e4, 2.5e4), "FSC.W" = c(8e4, 9e4, 1.5e5, 1.4e5)) # define gate

ggcyto(gs_DS096[[1]], aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 200) +
  geom_gate(g_singlets_DS096) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size height vs cell size width and singlet cell gate. One exemplary sample.* 

```{r fig_singlets_DS096, fig.width=9, fig.height=6}
# Apply the gate to all data
gs_pop_add(gs_DS096, g_singlets_DS096, parent = "Debris")
recompute(gs_DS096) 

ggcyto(gs_DS096, aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Live cells (fixed)

Define the gate on live/dead (fixed) cells (BV421 vs FSC-A): Exclude the upper data points and those data point that fall at/off the right edges of the plot
```{r live_DS096, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_live_DS096 <- polygonGate(filterId = "Live", "FSC.A" = c(4.5e4, 1.8e5, 1.8e5, 4.5e4), "BV421.A" = c(5e2, 5e2, 2e5, 2e5)) # define gate

ggcyto(gs_DS096[[2]], aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 200) +
  geom_gate(g_live_DS096) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e0, 5e5)) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs live/death stain and live cell gate. One exemplary sample.* 

```{r fig_live_DS096, fig.width=9, fig.height=6}
# Apply the gate to all data
gs_pop_add(gs_DS096, g_live_DS096, parent = "Singlets")
recompute(gs_DS096)

ggcyto(gs_DS096, aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e2, 5e5)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Summary

```{r gating_DS096}
# Remove previous file if it exist
if(file.exists(paste0("output/", "gated_data_DS096"))) {
  unlink(paste0("output/", "gated_data_DS096"), recursive = TRUE)
}

# Save dataset
save_gs(gs_DS096, path = paste0("output/", "gated_data_DS096"))

gc()

# Gating strategy
plot(gs_DS096, bool = TRUE)
```
***Figure:** Gating strategy.* 


### Population statistics

```{r cell_counts_DS096}
# Get cell counts
counts_DS096 <- gs_pop_get_count_fast(gs_DS096)
counts_DS096 <- merge(counts_DS096, pData(fs_DS096), by = "name")
counts_DS096$PercentParent <- (counts_DS096$Count / counts_DS096$ParentCount) * 100

# Calculate percentage from root
counts_root_DS096 <- counts_DS096 %>% filter(Parent == "root") %>% select(name, RootCount = ParentCount)
counts_DS096 <- left_join(counts_DS096, counts_root_DS096)
counts_DS096$PercentRoot <- (counts_DS096$Count / counts_DS096$RootCount) * 100

# Save the number of cells per well per gate as .csv file
counts_save_DS096 <- counts_DS096[ , c("plateID", "wellID", "name", "Population", "Count", "ParentCount", "PercentParent", "RootCount", "PercentRoot")]
write_csv(counts_save_DS096, file = "output/gated_counts_DS096.csv")
```

```{r fig_cells_DS096, fig.width=6, fig.height=4}
counts_final_DS096 <- subset(counts_DS096, Population == "/Debris/Singlets/Live")
raw_map(data = counts_final_DS096$Count, well = counts_final_DS096$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts") +
  theme_bw() +
  textsize
```
***Figure:** Number of live single cells after gating (counts per sample/well).* 

```{r live_cells_DS096}
percent_live_DS096 <- subset(counts_DS096, Population == "/Debris/Singlets/Live")[, c("name", "plateID", "wellID", "PercentRoot")]

# Add metadata per well from custom .csv file
metadata_DS096 <- read_csv("data/DS096_LinQuadGradient_HighConc/metadata_plate_DS096.csv")
percent_live_DS096 <- left_join(percent_live_DS096, metadata_DS096)
```

```{r fig_live_percent_DS096, fig.width=4, fig.height=4}
ggplot(subset(percent_live_DS096, staining == "yes"), aes(x = time_min, y = PercentRoot)) +
  geom_point(aes(color = factor(stim_description)), size = 2) +
  ylim(0, 100) +
  scale_x_continuous() +
  scale_color_manual(
    values = colors_dark9[1:5],
    breaks = rev(unique(percent_live_DS096$stim_description)),
    name = "",
  ) +
  labs(y = "Percentage live single \ncells from root (%)", x = "Stimulation time (min)") +
  theme_bw() +
  theme(legend.position = "bottom", legend.justification = "right") +
  guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize
```
***Figure:** Percentage of live single cells from root.*



## DS097: LinGradient_LowConc

### Data

Read the .fcs files and create a FlowSet object with metadata
```{r data_DS097}
# Read files with the FlowSet function
fs_DS097 <- read.flowSet(path = "data/DS097_LinGradient_LowConc/fcs", pattern = ".fcs", alter.names = T)
```

```{r metadata_DS097}
# Extract information on wellID, row and column from the file name
# Format of file name: wellID_number_date_time.fcs
pData(fs_DS097)$wellID <- gsub("(.*)_.*_.*_.*.fcs", "\\1", sampleNames(fs_DS097))
pData(fs_DS097)$rowID <- gsub("(.).*", "\\1", pData(fs_DS097)$wellID)
pData(fs_DS097)$colID <- as.numeric(gsub(".(.*)", "\\1", pData(fs_DS097)$wellID))
pData(fs_DS097)$expID <- "DS097"
pData(fs_DS097)$plateID <- "A"

kable(pData(fs_DS097) %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Debris

Define the gate on debris (SSC-A vs FSC-A): Exclude the lower left data points and those data point that fall at/off the upper and right edges of the plot
```{r debris_DS097, fig.width=5, fig.height=4}
# Create a GatingSet object from the FlowSet object
gs_DS097 <- GatingSet(fs_DS097)

# Manually adjust the numbers and check in the graph to set the right gate
g_debris_DS097 <- polygonGate(filterId = "Debris", "FSC.A" = c(4e4, 26e4, 26e4, 1e5), "SSC.A" = c(1e4, 1e4, 26e4, 26e4)) # define gate

ggcyto(gs_DS097[[1]], aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 200) +
  geom_gate(g_debris_DS097) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs cell complexity and debris gate. One exemplary sample.*  

```{r fig_debris_DS097, fig.width=9, fig.height=5}
# Apply the gate to all data
gs_pop_add(gs_DS097, g_debris_DS097)
recompute(gs_DS097)

ggcyto(gs_DS097, aes(x = FSC.A, y = SSC.A), subset = "root") +
  geom_hex(bins = 100) +
  geom_gate("Debris") +
  geom_stats(adjust = 0.8) +
  ggcyto_par_set(limits = "instrument" ) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Cell complexity (SSC-A)", title = "Non-debris from root") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Singlets

Define the gate on singlets (FSC-W vs FSC-H): Exclude all data points that do not fall in the mass of data points
```{r singlets_DS097, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_singlets_DS097 <- polygonGate(filterId = "Singlets", "FSC.H" = c(3e4, 6e4, 8.5e4, 2.5e4), "FSC.W" = c(8e4, 9e4, 1.4e5, 1.4e5)) # define gate

ggcyto(gs_DS097[[1]], aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 200) +
  geom_gate(g_singlets_DS097) +
  ggcyto_par_set(limits = "instrument") +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size height vs cell size width and singlet cell gate. One exemplary sample.* 

```{r fig_singlets_DS097, fig.width=9, fig.height=5}
# Apply the gate to all data
gs_pop_add(gs_DS097, g_singlets_DS097, parent = "Debris")
recompute(gs_DS097) 

ggcyto(gs_DS097, aes(x = FSC.H, y = FSC.W), subset = "Debris") +
  geom_hex(bins = 100) +
  geom_gate("Singlets") +
  geom_stats(adjust = c(1.5, 0)) +
  ggcyto_par_set(limits = "instrument") +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size height (FSC-H)", y = "Cell size width (FSC-W)", title = "Singlets from non-debris") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Live cells (fixed)

Define the gate on live/dead (fixed) cells (BV421 vs FSC-A): Exclude the upper data points and those data point that fall at/off the right edges of the plot
```{r live_DS097, fig.width=5, fig.height=4}
# Manually adjust the numbers and check in the graph to set right gate
g_live_DS097 <- polygonGate(filterId = "Live", "FSC.A" = c(4.5e4, 1.8e5, 1.8e5, 4.5e4), "BV421.A" = c(5e2, 5e2, 3e4, 1e4)) # define gate

ggcyto(gs_DS097[[1]], aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 200) +
  geom_gate(g_live_DS097) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e0, 1e5)) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)") +
  theme_bw() +
  textsize
```
***Figure:** Cell size vs live/death stain and live cell gate. One exemplary sample.* 

```{r fig_live_DS097, fig.width=9, fig.height=6}
# Apply the gate to all data
gs_pop_add(gs_DS097, g_live_DS097, parent = "Singlets")
recompute(gs_DS097) 

ggcyto(gs_DS097, aes(x = FSC.A, y = BV421.A), subset = "Singlets") +
  geom_hex(bins = 100) +
  geom_gate("Live") +
  geom_stats(adjust = 0.8) +
  scale_x_log10() +
  scale_y_log10(limits = c(5e2, 5e4)) +
  facet_grid(vars(rowID), vars(factor(colID, levels = col_order))) +
  labs(x = "Cell size (FSC-A)", y = "Live/death stain (BV421-A)", title = "Live cells from singlets") +
  theme_bw() +
  theme(legend.position = "none") + 
  textsize
```


### Summary

```{r gating_DS097}
# Remove previous file if it exist
if(file.exists(paste0("output/", "gated_data_DS097"))) {
  unlink(paste0("output/", "gated_data_DS097"), recursive = TRUE)
}

# Save dataset
save_gs(gs_DS097, path = paste0("output/", "gated_data_DS097"))

gc()

# Gating strategy
plot(gs_DS097, bool = TRUE)
```
***Figure:** Gating strategy.* 


### Population statistics

```{r cell_counts_DS097}
# Get cell counts
counts_DS097 <- gs_pop_get_count_fast(gs_DS097)
counts_DS097 <- merge(counts_DS097, pData(fs_DS097), by = "name")
counts_DS097$PercentParent <- (counts_DS097$Count / counts_DS097$ParentCount) * 100

# Calculate percentage from root
counts_root_DS097 <- counts_DS097 %>% filter(Parent == "root") %>% select(name, RootCount = ParentCount)
counts_DS097 <- left_join(counts_DS097, counts_root_DS097)
counts_DS097$PercentRoot <- (counts_DS097$Count / counts_DS097$RootCount) * 100

# Save the number of cells per well per gate as .csv file
counts_save_DS097 <- counts_DS097[ , c("plateID", "wellID", "name", "Population", "Count", "ParentCount", "PercentParent", "RootCount", "PercentRoot")]
write_csv(counts_save_DS097, file = "output/gated_counts_DS097.csv")
```

```{r fig_cells_DS097, fig.width=6, fig.height=4}
counts_final_DS097 <- subset(counts_DS097, Population == "/Debris/Singlets/Live")
raw_map(data = counts_final_DS097$Count, well = counts_final_DS097$wellID, plate = 96, size = 10) +
  scale_fill_viridis() +
  labs(title = "Single cell counts") +
  theme_bw() +
  textsize
```
***Figure:** Number of live single cells after gating (counts per sample/well).* 

```{r live_cells_DS097}
percent_live_DS097 <- subset(counts_DS097, Population == "/Debris/Singlets/Live")[, c("name", "plateID", "wellID", "PercentRoot")]

# Add metadata per well from custom .csv file
metadata_DS097 <- read_csv("data/DS097_LinGradient_LowConc/metadata_plate_DS097.csv")
percent_live_DS097 <- left_join(percent_live_DS097, metadata_DS097)
```

```{r fig_live_percent_DS097, fig.width=4, fig.height=4}
ggplot(subset(percent_live_DS097, staining == "yes"), aes(x = time_min, y = PercentRoot)) +
  geom_point(aes(color = factor(stim_description)), size = 2) +
  ylim(0, 100) +
  scale_x_continuous() +
  scale_color_manual(
    values = colors_dark9[1:5],
    breaks = rev(unique(percent_live_DS097$stim_description)),
    name = "",
  ) +
  labs(y = "Percentage live single \ncells from root (%)", x = "Stimulation time (min)") +
  theme_bw() +
  theme(legend.position = "bottom", legend.justification = "right") +
  guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
  textsize
```
***Figure:** Percentage of live single cells from root.*
