---
title: "Annotation of gated data"
author: "mwitmond"
date: "2023-03-08"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 3
    code_folding: hide
editor_options:
  chunk_output_type: console
---


## Set-up

```{r setup, message=F, warning=F}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_FACS.R", local = knitr::knit_global())
```


## DS085: LinGradient_Conc

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS085}
gs_DS085 <- load_gs(paste0("output/", "gated_data_DS085"))

gated_pops_DS085 <- gs_get_pop_paths(gs_DS085, path = "auto")
cs_DS085 <- gs_pop_get_data(gs_DS085, tail(gated_pops_DS085, 1))

# Remove all zero values from df in order to perform log transformations
df_DS085 <- fortify(cs_DS085)
df_DS085[df_DS085 <= 0] <- NA

# Select only columns that are needed
df_DS085 <- df_DS085[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS085}
# Add metadata per well from custom .csv file
metadata_DS085 <- read_csv("data/DS085_LinGradient_Conc/metadata_plate_DS085.csv")

# Change columns into character if necessary
metadata_DS085$colID <- as.character(metadata_DS085$colID)

df_DS085 <- left_join(df_DS085, metadata_DS085)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS085 <- df_DS085 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS085 <- left_join(df_DS085, counts_DS085)
# df_DS085 <- df_DS085[df_DS085$sample_cell_count > 5000, ]
remove_wells_DS085 <- df_DS085 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_DS085 <- df_DS085 %>%
  left_join(remove_wells_DS085) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))

gc()

# kable(df_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS085}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS085 <- c("expID", "plateID", "wellID", "sample", "stimulus", "conc_final", "stim_profile", "gradient_duration", "stim_description", "stim_descrip_short", "time_min", "time_point", "after_end", "conc_at_time_mM", "cumulative_exposure", "staining", "panel", "sample_cell_count") # include all metadata columns
         
df_PE_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS085 <- list(df_PE_DS085, df_AF647_DS085, df_AF488_DS085, df_BV421_DS085) %>% reduce(full_join)

gc()

# kable(df_tidy_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS085}
# Remove pBTK values >1.4e4 of the gradient sample at t = 0 min due to cell spillover between adjacent wells
df_tidy_DS085 <- df_tidy_DS085 %>%
  filter(!(protein == "pBTK (Y223)" & stim_profile == "gradient" & time_point == "0 min" & fluorescence > 1.4e4))

data_info_DS085 <- df_tidy_DS085 %>%
  filter(time_point == "0 min") %>% 
  group_by(plateID, stim_description, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS085 <- left_join(df_tidy_DS085, data_info_DS085)

# Create dataframe with percentage ON for each condition
data_total_DS085 <- df_tidy_DS085 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS085 <- df_tidy_DS085 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS085 <- left_join(data_total_DS085, data_on_DS085) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS085 <- left_join(df_tidy_DS085, data_counts_DS085)

gc()

kable(df_tidy_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS085}
# Calculate median values for each sample
medians_DS085 <- df_tidy_DS085 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS085 <- left_join(medians_DS085, distinct(select(df_tidy_DS085, cols_meta_DS085))) %>%
  left_join(data_counts_DS085)

gc()

# kable(medians_tidy_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS085}
write.csv(df_tidy_DS085, file = "output/annotated_data/annotated_data_tidy_DS085.csv", row.names = F)

write.csv(medians_tidy_DS085, file = "output/annotated_data/annotated_medians_tidy_DS085.csv", row.names = F)

# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS085"))
gc()
```



## DS095: DetailedStep_Conc

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS095}
gs_DS095 <- load_gs(paste0("output/", "gated_data_DS095"))

gated_pops_DS095 <- gs_get_pop_paths(gs_DS095, path = "auto")
cs_DS095 <- gs_pop_get_data(gs_DS095, tail(gated_pops_DS095, 1))

# Remove all zero values from df in order to perform log transformations
df_DS095 <- fortify(cs_DS095)
df_DS095[df_DS095 <= 0] <- NA

# Select only columns that are needed
df_DS095 <- df_DS095[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS095}
# Add metadata per well from custom .csv file
metadata_DS095 <- read_csv("data/DS095_DetailedStep_Conc/metadata_plate_DS095.csv")

# Change columns into character if necessary
metadata_DS095$colID <- as.character(metadata_DS095$colID)

df_DS095 <- left_join(df_DS095, metadata_DS095)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS095 <- df_DS095 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS095 <- left_join(df_DS095, counts_DS095)
# df_DS095 <- df_DS095[df_DS095$sample_cell_count > 5000, ]
remove_wells_DS095 <- df_DS095 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_DS095 <- df_DS095 %>%
  left_join(remove_wells_DS095) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))

gc()

# kable(df_DS095 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS095}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS095 <- c("expID", "plateID", "wellID", "sample", "stimulus", "H2O2_conc_mM", "time_min", "time_point", "cumulative_exposure", "replicate", "stim_description", "staining", "panel", "sample_cell_count") # include all metadata columns

df_PE_DS095 <- df_DS095 %>% 
  select(all_of(cols_meta_DS095), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS095 <- df_DS095 %>% 
  select(all_of(cols_meta_DS095), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS095 <- df_DS095 %>% 
  select(all_of(cols_meta_DS095), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS095 <- df_DS095 %>% 
  select(all_of(cols_meta_DS095), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS095 <- list(df_PE_DS095, df_AF647_DS095, df_AF488_DS095, df_BV421_DS095) %>% reduce(full_join)

gc()

# kable(df_tidy_DS095 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS095}
# Get the value for each conc where in sample t = 0 2.5% of cells are higher
data_info_DS095 <- df_tidy_DS095 %>%
  filter(time_point == "0 min") %>%
  group_by(plateID, H2O2_conc_mM, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS095 <- left_join(df_tidy_DS095, data_info_DS095)

# Create dataframe with percentage ON for each condition
data_total_DS095 <- df_tidy_DS095 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS095 <- df_tidy_DS095 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS095 <- left_join(data_total_DS095, data_on_DS095) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS095 <- left_join(df_tidy_DS095, data_counts_DS095)

gc()

kable(df_tidy_DS095 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS095}
# Calculate median values for each sample
medians_DS095 <- df_tidy_DS095 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS095 <- left_join(medians_DS095, distinct(select(df_tidy_DS095, cols_meta_DS095))) %>%
  left_join(data_counts_DS095)

gc()

# kable(medians_tidy_DS095 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r medians_rep_DS095}
# Make a dataframe with means and standard deviation of replicates
medians_avg_DS095 <- medians_tidy_DS095 %>%
  dplyr::group_by(H2O2_conc_mM, time_point, protein) %>%
  summarise(
    fluorescence_sd = sd(fluorescence_median, na.rm = T),
    fluorescence = mean(fluorescence_median, na.rm = T), 
    percent_sd = sd(percent_on, na.rm = T),
    percent_on = mean(percent_on, na.rm = T)
    )

medians_avg_DS095 <- left_join(medians_avg_DS095, select(medians_tidy_DS095, c(expID, sample, stimulus, H2O2_conc_mM, time_min, time_point, cumulative_exposure, staining, panel, fluor, protein)), multiple = "all") %>%
  select(-c("plateID", "wellID")) %>%
  # select(stimulus, stim_profile, gradient_duration, stim_description, time_min, time_point, conc_at_time, cum_exposure, staining, panel,fluor, protein, fluorescence, fluorescence_sd, fluorescence_zero, FC, FC_sd, log2FC, log2FC_sd) %>% #, fluorescence_norm, fluorescence_norm_sd, fluorescence_norm_zero, FC_norm, FC_norm_sd, log2FC_norm, log2FC_norm_sd
  distinct() %>% 
  mutate(stim_description = paste(H2O2_conc_mM, "mM -", time_point))

gc()

# kable(medians_avg_DS095 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS095}
write.csv(df_tidy_DS095, file = "output/annotated_data/annotated_data_tidy_DS095.csv", row.names = F)

write.csv(medians_tidy_DS095, file = "output/annotated_data/annotated_medians_tidy_DS095.csv", row.names = F)

write.csv(medians_avg_DS095, file = "output/annotated_data/annotated_medians_avg_rep_DS095.csv", row.names = F)

# Remove files to clear up memory
rm(list = ls(pattern = "_DS095"))
gc()
```



## DS096: LinQuadGradient_HighConc

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS096}
gs_DS096 <- load_gs(paste0("output/", "gated_data_DS096"))

gated_pops_DS096 <- gs_get_pop_paths(gs_DS096, path = "auto")
cs_DS096 <- gs_pop_get_data(gs_DS096, tail(gated_pops_DS096, 1))

# Remove all zero values from df in order to perform log transformations
df_DS096 <- fortify(cs_DS096)
df_DS096[df_DS096 <= 0] <- NA

# Select only columns that are needed
df_DS096 <- df_DS096[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS096}
# Add metadata per well from custom .csv file
metadata_DS096 <- read_csv("data/DS096_LinQuadGradient_HighConc/metadata_plate_DS096.csv")

# Change columns into character if necessary
metadata_DS096$colID <- as.character(metadata_DS096$colID)

df_DS096 <- left_join(df_DS096, metadata_DS096)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS096 <- df_DS096 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS096 <- left_join(df_DS096, counts_DS096)
# df_DS096 <- df_DS096[df_DS096$sample_cell_count > 5000, ]
remove_wells_DS096 <- df_DS096 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_DS096 <- df_DS096 %>%
  left_join(remove_wells_DS096) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))

gc()

# kable(df_DS096 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS096}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS096 <- c("expID", "plateID", "wellID", "sample", "stimulus", "conc_final", "stim_profile", "gradient_duration", "stim_description", "stim_descrip_short", "time_min", "time_point", "after_end", "conc_at_time_mM", "cumulative_exposure", "staining", "panel", "sample_cell_count") # include all metadata columns

df_PE_DS096 <- df_DS096 %>% 
  select(cols_meta_DS096, protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS096 <- df_DS096 %>% 
  select(cols_meta_DS096, protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS096 <- df_DS096 %>% 
  select(cols_meta_DS096, protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS096 <- df_DS096 %>% 
  select(cols_meta_DS096, protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS096 <- list(df_PE_DS096, df_AF647_DS096, df_AF488_DS096, df_BV421_DS096) %>% reduce(full_join)

gc()

# kable(df_tidy_DS096 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS096}
data_info_DS096 <- df_tidy_DS096 %>%
  filter(time_point == "0 min") %>% 
  group_by(plateID, stim_description, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS096 <- left_join(df_tidy_DS096, data_info_DS096)

# Create dataframe with percentage ON for each condition
data_total_DS096 <- df_tidy_DS096 %>%
  group_by(wellID, protein) %>%
  count(name = "count_total")

data_on_DS096 <- df_tidy_DS096 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(wellID, protein) %>%
  count(name = "count_on")

data_counts_DS096 <- left_join(data_total_DS096, data_on_DS096) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS096 <- left_join(df_tidy_DS096, data_counts_DS096)

gc()

kable(df_tidy_DS096 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS096}
# Calculate median values for each sample
medians_DS096 <- df_tidy_DS096 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)
medians_tidy_DS096 <- left_join(medians_DS096, distinct(select(df_tidy_DS096, cols_meta_DS096))) %>%
  left_join(data_counts_DS096)

gc()

# kable(medians_tidy_DS096 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS096}
write.csv(df_tidy_DS096, file = "output/annotated_data/annotated_data_tidy_DS096.csv", row.names = F)

write.csv(medians_tidy_DS096, file = "output/annotated_data/annotated_medians_tidy_DS096.csv", row.names = F)

# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS096"))
gc()
```



## DS097: LinGradient_LowConc

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS097}
gs_DS097 <- load_gs(paste0("output/", "gated_data_DS097"))

gated_pops_DS097 <- gs_get_pop_paths(gs_DS097, path = "auto")
cs_DS097 <- gs_pop_get_data(gs_DS097, tail(gated_pops_DS097, 1))

# Remove all zero values from df in order to perform log transformations
df_DS097 <- fortify(cs_DS097)
df_DS097[df_DS097 <= 0] <- NA

# Select only columns that are needed
df_DS097 <- df_DS097[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS097}
# Add metadata per well from custom .csv file
metadata_DS097 <- read_csv("data/DS097_LinGradient_LowConc/metadata_plate_DS097.csv")

# Change columns into character if necessary
metadata_DS097$colID <- as.character(metadata_DS097$colID)

df_DS097 <- left_join(df_DS097, metadata_DS097)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS097 <- df_DS097 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS097 <- left_join(df_DS097, counts_DS097)
# df_DS097 <- df_DS097[df_DS097$sample_cell_count > 5000, ]
remove_wells_DS097 <- df_DS097 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_DS097 <- df_DS097 %>%
  left_join(remove_wells_DS097) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))

gc()

# kable(df_DS097 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS097}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS097 <- c("expID", "plateID", "wellID", "sample", "stimulus", "conc_final", "stim_profile", "gradient_duration", "stim_description", "stim_descrip_short", "time_min", "time_point", "after_end", "conc_at_time_mM", "cumulative_exposure", "staining", "panel", "sample_cell_count") # include all metadata columns

df_PE_DS097 <- df_DS097 %>% 
  select(cols_meta_DS097, protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS097 <- df_DS097 %>% 
  select(cols_meta_DS097, protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS097 <- df_DS097 %>% 
  select(cols_meta_DS097, protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS097 <- df_DS097 %>% 
  select(cols_meta_DS097, protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS097 <- list(df_PE_DS097, df_AF647_DS097, df_AF488_DS097, df_BV421_DS097) %>% reduce(full_join)

gc()

# kable(df_tidy_DS097 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS097}
data_info_DS097 <- df_tidy_DS097 %>%
  filter(time_point == "0 min") %>% 
  group_by(plateID, stim_description, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS097 <- left_join(df_tidy_DS097, data_info_DS097)

# Create dataframe with percentage ON for each condition
data_total_DS097 <- df_tidy_DS097 %>%
  group_by(wellID, protein) %>%
  count(name = "count_total")

data_on_DS097 <- df_tidy_DS097 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(wellID, protein) %>%
  count(name = "count_on")

data_counts_DS097 <- left_join(data_total_DS097, data_on_DS097) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS097 <- left_join(df_tidy_DS097, data_counts_DS097)

gc()

kable(df_tidy_DS097 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS097}
# Calculate median values for each sample
medians_DS097 <- df_tidy_DS097 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)
medians_tidy_DS097 <- left_join(medians_DS097, distinct(select(df_tidy_DS097, cols_meta_DS097))) %>%
  left_join(data_counts_DS097)

gc()

# kable(medians_tidy_DS097 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS097}
write.csv(df_tidy_DS097, file = "output/annotated_data/annotated_data_tidy_DS097.csv", row.names = F)

write.csv(medians_tidy_DS097, file = "output/annotated_data/annotated_medians_tidy_DS097.csv", row.names = F)

# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS097"))
gc()
```
