---
title: "Annotation of gated data"
author: "mwitmond"
date: "2023-03-08"
output:
  workflowr::wflow_html:
    toc: TRUE
    code_folding: hide
editor_options:
  chunk_output_type: console
---


## Set-up

```{r setup, message=F, warning=F}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_FACS.R", local = knitr::knit_global())
```


## DS.085: Linear gradients with conc-based sampling

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS085}
gs_DS085 <- load_gs(paste0("output/", "gated_data_DS085"))

gated_pops_DS085 <- gs_get_pop_paths(gs_DS085, path = "auto")
cs_DS085 <- gs_pop_get_data(gs_DS085, tail(gated_pops_DS085, 1))

# Remove all zero values from df in order to perform log transformations
df_DS085 <- fortify(cs_DS085)
df_DS085[df_DS085 <= 0] <- NA

# Select only columns that are needed
df_DS085 <- df_DS085[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]
```

```{r metadata_DS085}
# Add metadata per well from custom .csv file
metadata_DS085 <- read_csv("data/DS085_LinGradient_Conc/metadata_plate_DS085.csv")

# Change columns into character if necessary
metadata_DS085$colID <- as.character(metadata_DS085$colID)

df_DS085 <- left_join(df_DS085, metadata_DS085)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS085 <- df_DS085 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS085 <- left_join(df_DS085, counts_DS085)
# df_DS085 <- df_DS085[df_DS085$sample_cell_count > 5000, ]
remove_wells_DS085 <- df_DS085 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_DS085 <- df_DS085 %>%
  left_join(remove_wells_DS085) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))
  
kable(df_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


## Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS085}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS085 <- c("expID", "plateID", "wellID", "sample", "stimulus", "stim_profile", "gradient_duration", "stim_description", "time_min", "time_point", "conc_at_time_mM", "cumulative_exposure", "staining", "panel", "sample_cell_count") # include all metadata columns

df_PE_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS085 <- df_DS085 %>% 
  select(all_of(cols_meta_DS085), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS085 <- list(df_PE_DS085, df_AF647_DS085, df_AF488_DS085, df_BV421_DS085) %>% reduce(full_join)

kable(df_tidy_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS085}
data_info_DS085 <- df_tidy_DS085 %>%
  filter(time_point == "0 min") %>% 
  group_by(plateID, stim_description, protein) %>%
  summarise(zero_quant95 = quantile(fluorescence, c(0.95), na.rm = T))

df_tidy_DS085 <- left_join(df_tidy_DS085, data_info_DS085)

# Create dataframe with percentage ON for each condition
data_total_DS085 <- df_tidy_DS085 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS085 <- df_tidy_DS085 %>%
  filter((fluorescence - zero_quant95) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS085 <- left_join(data_total_DS085, data_on_DS085) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS085 <- left_join(df_tidy_DS085, data_counts_DS085)
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS085}
# Calculate median values for each sample
medians_DS085 <- df_tidy_DS085 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS085 <- left_join(medians_DS085, distinct(select(df_tidy_DS085, cols_meta_DS085))) %>%
  left_join(data_counts_DS085)

# # Transform data into fold change (FC) to t = 0 min and log2(FC)
# medians_zero_DS085 <- medians_tidy_DS085 %>% 
#   filter(time_point == "0 min") %>% 
#   select(
#     plateID, 
#     stim_description_rep, 
#     protein,
#     fluorescence_zero = fluorescence_median
#     )
# medians_tidy_DS085 <- left_join(medians_tidy_DS085, medians_zero_DS085[, c("plateID", "stim_description_rep", "protein", "fluorescence_zero")])
# 
# medians_tidy_DS085 <- medians_tidy_DS085 %>%
#   mutate(fluorescence = fluorescence_median, 
#          FC = (fluorescence / fluorescence_zero), 
#          log2FC = (log2(FC)), 
#          ) %>%
#   select(-c(fluorescence_median)) 

kable(medians_tidy_DS085 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS085}
write.csv(df_tidy_DS085, file = "output/annotated_data_tidy_DS085.csv", row.names = F)

write.csv(medians_tidy_DS085, file = "output/annotated_medians_tidy_DS085.csv", row.names = F)
```




## Bas.013: Linear gradients with cum exp-based sampling

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_Bas013}
gs_Bas013 <- load_gs(paste0("output/", "gated_data_Bas013"))

gated_pops_Bas013 <- gs_get_pop_paths(gs_Bas013, path = "auto")
cs_Bas013 <- gs_pop_get_data(gs_Bas013, tail(gated_pops_Bas013, 1))

# Remove all zero values from df in order to perform log transformations
df_Bas013 <- fortify(cs_Bas013)
df_Bas013[df_Bas013 <= 0] <- NA

# Select only columns that are needed
df_Bas013 <- df_Bas013[ , c("name", "expID", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]
```

```{r metadata_Bas013}
# Add metadata per well from custom .csv file
metadata_Bas013 <- read_csv("data/Bas013_LinGradient_CumExp/metadata_plate_Bas013.csv")

# Change columns into character if necessary
metadata_Bas013$colID <- as.character(metadata_Bas013$colID)

df_Bas013 <- left_join(df_Bas013, metadata_Bas013)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_Bas013 <- df_Bas013 %>% count(plateID, wellID, name = "sample_cell_count")
df_Bas013 <- left_join(df_Bas013, counts_Bas013)
# df_Bas013 <- df_Bas013[df_Bas013$sample_cell_count > 5000, ]
remove_wells_Bas013 <- df_Bas013 %>%
  filter(sample_cell_count < 5000) %>%
  select(plateID, wellID, time_min) %>% 
  distinct() %>%
  filter(time_min > 0) %>%
  select(plateID, wellID) %>%
  mutate(wellID_rem = wellID)
df_Bas013 <- df_Bas013 %>%
  left_join(remove_wells_Bas013) %>%
  replace_na(list(wellID_rem = "x")) %>%
  filter(wellID_rem == "x") %>%
  select(-c(wellID_rem))

kable(df_Bas013 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


## Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_Bas013}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_Bas013 <- c("expID", "plateID", "wellID", "sample", "stimulus", "stim_profile", "gradient_duration", "stim_description", "time_min", "time_point", "conc_at_time_mM", "cumulative_exposure", "staining", "panel", "sample_cell_count") # include all metadata columns

df_PE_Bas013 <- df_Bas013 %>% 
  select(cols_meta_Bas013, protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_Bas013 <- df_Bas013 %>% 
  select(cols_meta_Bas013, protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_Bas013 <- df_Bas013 %>% 
  select(cols_meta_Bas013, protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_Bas013 <- df_Bas013 %>% 
  select(cols_meta_Bas013, protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_Bas013 <- list(df_PE_Bas013, df_AF647_Bas013, df_AF488_Bas013, df_BV421_Bas013) %>% reduce(full_join)

kable(df_tidy_Bas013 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_Bas013}
data_info_Bas013 <- df_tidy_Bas013 %>%
  filter(time_point == "0 min") %>% 
  group_by(plateID, stim_description, protein) %>%
  summarise(zero_quant95 = quantile(fluorescence, c(0.95), na.rm = T))

df_tidy_Bas013 <- left_join(df_tidy_Bas013, data_info_Bas013)

# Create dataframe with percentage ON for each condition
data_total_Bas013 <- df_tidy_Bas013 %>%
  group_by(wellID, protein) %>%
  count(name = "count_total")

data_on_Bas013 <- df_tidy_Bas013 %>%
  filter((fluorescence - zero_quant95) > 0) %>%
  group_by(wellID, protein) %>%
  count(name = "count_on")

data_counts_Bas013 <- left_join(data_total_Bas013, data_on_Bas013) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_Bas013 <- left_join(df_tidy_Bas013, data_counts_Bas013)
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_Bas013}
# Calculate median values for each sample
medians_Bas013 <- df_tidy_Bas013 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)
medians_tidy_Bas013 <- left_join(medians_Bas013, distinct(select(df_tidy_Bas013, cols_meta_Bas013))) %>%
  left_join(data_counts_Bas013)

# # Transform data into fold change (FC) to t = 0 min and log2(FC)
# medians_zero_Bas013 <- medians_tidy_Bas013 %>% 
#   filter(time_point == "0 min") %>% 
#   select(
#     plateID, 
#     stim_description_rep, 
#     protein,
#     fluorescence_zero = fluorescence_median
#     )
# medians_tidy_Bas013 <- left_join(medians_tidy_Bas013, medians_zero_Bas013[, c("plateID", "stim_description_rep", "protein", "fluorescence_zero")])
# 
# medians_tidy_Bas013 <- medians_tidy_Bas013 %>%
#   mutate(fluorescence = fluorescence_median, 
#          FC = (fluorescence / fluorescence_zero), 
#          log2FC = (log2(FC)), 
#          ) %>%
#   select(-c(fluorescence_median)) 

kable(medians_tidy_Bas013 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_Bas013}
write.csv(df_tidy_Bas013, file = "output/annotated_data_tidy_Bas013.csv", row.names = F)

write.csv(medians_tidy_Bas013, file = "output/annotated_medians_tidy_Bas013.csv", row.names = F)
```
