---
title: "Gradient input profile generation"
author: "mwitmond"
date: "2023-08-17"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 3
    code_folding: hide
editor_options:
  chunk_output_type: console
---


## Set-up

```{r setup, message=F, warning=F}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_FACS.R", local = knitr::knit_global())
source("code/generate_stimulation_gradients.R", local = knitr::knit_global())
```

```{r fig_settings}
row_order = c("A", "B", "C", "D", "E", "F", "G", "H")
col_order = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
panel_labels <- c("a", "b", "c","d", "e", "f", "g", "h", "i", "j", "k", "l", "m")

textsize <- theme(axis.text = element_text(colour = "black", size = 11), #, face = "bold"
                  axis.title = element_text(colour = "black", size = 12), 
                  legend.title = element_text(colour = "black", size = 12),
                  # legend.title = element_blank(), 
                  legend.text = element_text(colour = "black", size = 11), 
                  strip.text.x = element_text(colour = "black", size = 12)
)

textsize_small <- theme(text = element_text(size = 8, family = "sans", colour = "black"), 
                        strip.text.x = element_text(size = 7)
)

colors_dark9 <- c("#4daf4a", "#984ea3", "#377eb8", "#ff7f00", "#ffff33", "#e41a1c", "#f781bf", "#a65628", "#999999")
colors_light12 <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5","#d9d9d9","#bc80bd","#ccebc5","#ffed6f")
colors_paired10 <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a", "#fb9a99", "#e31a1c")
colors_blue9 <- c("#f7fbff", "#deebf7", "#c6dbef", "#9ecae1", "#6baed6", "#4292c6", "#2171b5", "#08519c", "#08306b")
colors_red_blue8 <- c("#d73027", "#f46d43", "#fdae61", "#fee090", "#e0f3f8", "#abd9e9", "#74add1", "#4575b4")
colors_green_blue9 <- c("#f7fcf0","#e0f3db","#ccebc5","#a8ddb5","#7bccc4","#4eb3d3","#2b8cbe","#0868ac","#084081")
colors_grey9 <- c("#ffffff","#f0f0f0","#d9d9d9","#bdbdbd","#969696","#737373","#525252","#252525","#000000")
```



## DS085: LinGradient_Conc

Experimental parameters:

- Initial volume: 7.75 mL (8.0 mL before start, 0.25 mL sample t = 0 min)

- Gradient durations: 20 min, 60 min

- Stock stimulus concentration: 980 mM

- Final stimulus concentration: 5 mM

```{r parameters_DS085}
# Parameters
initial_volume <- 7.75*1e-3 # L
stimulus_concentration <- 980 # mM ## 1.3 # mg/mL
gradient_duration <- c(20, 60) # min
final_stimulus_concentration <- 5 # mM ## 10*1e-3 # g/mL
sample_during_gradient <- 7
sample_volume <- 0.00025 # L
```


### 20 min

```{r gradient_20min_DS085}
# Create sampling dataset and gradient profile
df_smpl <- create_df_sampling_uniform(N = sample_during_gradient,
                                      d_sample = sample_volume,
                                      dt = gradient_duration[1]*60/(sample_during_gradient+1),
                                      rate = 5000000,
                                      units = c("s", "L", "mkL/h"))

concentration <- function(t) {final_stimulus_concentration * t / gradient_duration[1]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[1],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                     parameter = "sampling_rate",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize

# fig_dV <- plot_gradient(linear_gradient, 
#                     parameter = "dV",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize

# fig_dS <- plot_gradient(linear_gradient, 
#                     parameter = "dS",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_20 <- plot_grid(fig_conc, fig_volume, fig_flow_rate, fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_20 <- ggdraw() + draw_label("20 min linear gradient", fontface = "bold")
fig_20 <- plot_grid(title_20, fig_20, ncol = 1, rel_heights = c(0.1, 1))
fig_20

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS085_LinGradient_Conc", 
                               paste(c("npf_DS085_linear_", 
                                       final_stimulus_concentration, "mM_", 
                                       gradient_duration[1], "min"), 
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```


### 60 min

```{r gradient_60min_DS085}
# Create sampling dataset and gradient profile
df_smpl <- create_df_sampling_uniform(N = sample_during_gradient,
                                      d_sample = sample_volume,
                                      dt = gradient_duration[2]*60/(sample_during_gradient+1),
                                      rate = 5000000,
                                      units = c("s", "L", "mkL/h"))

concentration <- function(t) {final_stimulus_concentration * t / gradient_duration[2]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[2],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                     parameter = "sampling_rate",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize

# fig_dV <- plot_gradient(linear_gradient, 
#                     parameter = "dV",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize

# fig_dS <- plot_gradient(linear_gradient, 
#                     parameter = "dS",
#                     V_unit = "mL",
#                     t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_60 <- plot_grid(fig_conc, fig_volume, fig_flow_rate, fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_60 <- ggdraw() + draw_label("60 min linear gradient", fontface = "bold")
fig_60 <- plot_grid(title_60, fig_60, ncol = 1, rel_heights = c(0.1, 1))
fig_60

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS085_LinGradient_Conc", 
                               paste(c("npf_DS085_linear_", 
                                       final_stimulus_concentration, "mM_", 
                                       gradient_duration[2], "min"), 
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```



## DS096: LinQuadGradient_HighConc

Experimental parameters:

- Initial volume: 7.25 mL (7.5 mL before start, 0.25 mL sample t = 0 min)

- Gradient durations: 20 min, 60 min

- Stock stimulus concentration: 1390 mM

- Final stimulus concentration: 10 mM

```{r parameters_DS096}
# Parameters
initial_volume <- 7.25*1e-3 # L
stimulus_concentration <- 139 # mM 
gradient_duration <- c(20, 60, 60) # min
final_stimulus_concentration <- 10 # mM
sample_during_gradient <- 7
sample_volume <- 0.00025 # L
```


### 20 min linear

```{r gradient_20min_DS096}
# Create sampling dataset and gradient profile
df_smpl20 <- read.csv2(file = "data/DS096_LinQuadGradient_HighConc/input_profiles_samples/linear_20_min.csv")

concentration <- function(t) {final_stimulus_concentration * t / gradient_duration[1]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[1],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl20, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(linear_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(linear_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_20 <- plot_grid(fig_conc, fig_volume, fig_flow_rate, fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_20 <- ggdraw() + draw_label("20 min linear gradient", fontface = "bold")
fig_20 <- plot_grid(title_20, fig_20, ncol = 1, rel_heights = c(0.1, 1))
fig_20

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS096_LinQuadGradient_HighConc", 
                               paste(c("npf_DS096_linear_", 
                                       final_stimulus_concentration, "mM_", 
                                       gradient_duration[1], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```


### 60 min linear

```{r gradient_60min_DS096}
# Create sampling dataset and gradient profile
df_smpl60lin <- read.csv2(file = "data/DS096_LinQuadGradient_HighConc/input_profiles_samples/linear_60_min.csv")

concentration <- function(t) {final_stimulus_concentration * t / gradient_duration[2]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[2],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl60lin, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(linear_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(linear_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_60 <- plot_grid(fig_conc, fig_volume, fig_flow_rate,   fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_60 <- ggdraw() + draw_label("60 min linear gradient", fontface = "bold")
fig_60 <- plot_grid(title_60, fig_60, ncol = 1, rel_heights = c(0.1, 1))
fig_60

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS096_LinQuadGradient_HighConc",
                               paste(c("npf_DS096_linear_",
                                       final_stimulus_concentration, "mM_",
                                       gradient_duration[2], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```


### 60 min quadratic

```{r gradient_60minquad_DS096}
# Create sampling dataset and gradient profile
df_smpl60quad <- read.csv2(file = "data/DS096_LinQuadGradient_HighConc/input_profiles_samples/quadratic_60_min.csv")

concentration_quad <- function(t) {4.62963e-5 * t^3} 
quadratic_gradient <- gradient(concentration_quad,
                               gradient_duration[3],
                               t_unit = "min", #s, ms, min, h
                               initial_volume, 
                               V_unit = "L", #L, mL, mkL, μL
                               df_smpl60quad, 
                               stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(quadratic_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(quadratic_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(quadratic_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(quadratic_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(quadratic_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(quadratic_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(quadratic_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_60q <- plot_grid(fig_conc, fig_volume, fig_flow_rate,   fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_60q <- ggdraw() + draw_label("60 min quadratic gradient", fontface = "bold")
fig_60q <- plot_grid(title_60q, fig_60q, ncol = 1, rel_heights = c(0.1, 1))
fig_60q

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS096_LinQuadGradient_HighConc",
                               paste(c("npf_DS096_quadratic_",
                                       final_stimulus_concentration, "mM_",
                                       gradient_duration[3], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```



## DS097: LinGradient_LowConc

Experimental parameters:

- Initial volume: 7.25 mL (7.5 mL before start, 0.25 mL sample t = 0 min)

- Gradient durations: 20 min, 60 min

- Stock stimulus concentration: 1390 mM

- Final stimulus concentration: 2.5 or 5 mM

```{r parameters}
# Parameters
initial_volume <- 7.25*1e-3 # L
stimulus_concentration <- 1390 # mM 
gradient_duration <- c(20, 60) # min
final_stimulus_concentration <- c(2.5, 5) # mM
sample_during_gradient <- 7
sample_volume <- 0.00025 # L
```


### 20 min linear 5 mM

```{r gradient_20min}
# Create sampling dataset and gradient profile
df_smpl20 <- read.csv2(file = "data/DS097_LinGradient_LowConc/input_profiles_samples/linear_20_min.csv")

concentration <- function(t) {final_stimulus_concentration[2] * t / gradient_duration[1]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[1],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl20,  
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(linear_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(linear_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_20 <- plot_grid(fig_conc, fig_volume, fig_flow_rate,   fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_20 <- ggdraw() + draw_label("20 min linear gradient", fontface = "bold")
fig_20 <- plot_grid(title_20, fig_20, ncol = 1, rel_heights = c(0.1, 1))
fig_20

# # Export gradient for Cetoni Nemesys pumps
# path_to_nfs_files <- file.path("output", "npf_DS.DynSign097_20_min_5mM")
# export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS097_LinGradient_LowConc", 
                               paste(c("npf_DS097_linear_", 
                                       final_stimulus_concentration[2], "mM_", 
                                       gradient_duration[1], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```

### 60 min linear 2.5 mM

```{r gradient_60min2.5mM}
# Create sampling dataset and gradient profile
df_smpl60 <- read.csv2(file = "data/DS097_LinGradient_LowConc/input_profiles_samples/linear_60_min.csv")

concentration <- function(t) {final_stimulus_concentration[1] * t / gradient_duration[2]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[2],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl60, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(linear_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(linear_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_60 <- plot_grid(fig_conc, fig_volume, fig_flow_rate,   fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_60 <- ggdraw() + draw_label("60 min linear gradient", fontface = "bold")
fig_60 <- plot_grid(title_60, fig_60, ncol = 1, rel_heights = c(0.1, 1))
fig_60

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS097_LinGradient_LowConc", 
                               paste(c("npf_DS097_linear_", 
                                       final_stimulus_concentration[1], "mM_", 
                                       gradient_duration[2], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```


### 60 min linear 5 mM

```{r gradient_60min5mM}
# Create sampling dataset and gradient profile
df_smpl60 <- read.csv2(file = "data/DS097_LinGradient_LowConc/input_profiles_samples/linear_60_min.csv")

concentration <- function(t) {final_stimulus_concentration[2] * t / gradient_duration[2]} 
linear_gradient <- gradient(concentration,
                            gradient_duration[2],
                            t_unit = "min", #s, ms, min, h
                            initial_volume, 
                            V_unit = "L", #L, mL, mkL, μL
                            df_smpl60, 
                            stimulus_concentration)

# Preview gradient profile
fig_conc <- plot_gradient(linear_gradient, 
                          parameter = "concentration",
                          V_unit = "L", #s, ms, min, h) +
                          t_unit = "min") + 
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Concentration (mM)", title = "Time vs concentration") +
  theme(legend.position = "none") +
  textsize

fig_volume <- plot_gradient(linear_gradient, 
                            parameter = "volume",
                            V_unit = "mL",
                            t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Volume (mL)", title = "Time vs volume") +
  theme(legend.position = "none") +
  textsize

fig_flow_rate <- plot_gradient(linear_gradient, 
                               parameter = "rate",
                               V_unit = "mL",
                               t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  labs(x = "Time (min)", y = "Flow rate", title = "Time vs flow rate") +
  theme(legend.position = "none") +
  textsize

fig_sampling_index <- plot_gradient(linear_gradient, 
                                    parameter = "sampling_index",
                                    V_unit = "L",
                                    t_unit = "min") + #s, ms, min, h) +
  theme_bw() +
  ylim(c(0, NA)) +
  labs(x = "Time (min)", y = "Sampling index", title = "Time vs sampling index") +
  theme(legend.position = "none") +
  textsize

# fig_sampling_rate <- plot_gradient(linear_gradient, 
#                                    parameter = "sampling_rate",
#                                    V_unit = "mL",
#                                    t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "Sampling rate", title = "Time vs sampling rate") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dV <- plot_gradient(linear_gradient, 
#                         parameter = "dV",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dV", title = "Time vs dV") +
#   theme(legend.position = "none") +
#   textsize
# 
# fig_dS <- plot_gradient(linear_gradient, 
#                         parameter = "dS",
#                         V_unit = "mL",
#                         t_unit = "min") + #s, ms, min, h) +
#   theme_bw() +
#   ylim(c(0, NA)) +
#   labs(x = "Time (min)", y = "dS", title = "Time vs dS") +
#   theme(legend.position = "none") +
#   textsize

fig_60 <- plot_grid(fig_conc, fig_volume, fig_flow_rate,   fig_sampling_index, labels = panel_labels, label_size = 15, ncol = 2, rel_widths =  c(1,1))
title_60 <- ggdraw() + draw_label("60 min linear gradient", fontface = "bold")
fig_60 <- plot_grid(title_60, fig_60, ncol = 1, rel_heights = c(0.1, 1))
fig_60

# Export gradient for Cetoni Nemesys pumps
path_to_nfs_files <- file.path("output/input_profiles/DS097_LinGradient_LowConc", 
                               paste(c("npf_DS097_linear_", 
                                       final_stimulus_concentration[2], "mM_", 
                                       gradient_duration[2], "min"),
                                     collapse = ""))
export_nemesys_profile_gradient(path_to_nfs_files, linear_gradient, n_sampling_pumps = 1)
```
